QPLIB: A Library of Quadratic Programming Instances

### 2017-01-23 QPLIB-2.3.tex
clear up listing of complete b&b solvers

The solvers in Table \ref{t:solvers} BB type methods are:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo}, {\sc LindoGlobal}, {\sc SCIP}, {\sc lgo\_bb}, which implement complete BB algorithms for QGQ;
 %
\item {\sc CPLEX}, which implements a complete BB algorithm for QGL;
%
 \item {\sc Knitro\_bb}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} which implement complete BB algorithms for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.

>>>>

The following solvers from Table \ref{t:solvers} implement complete BB algorithms for QGQ or some subclasses:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo API}, {\sc SCIP} for QGQ;
 %
\item {\sc CPLEX} for QGL and CGC;
%
 \item {\sc Knitro}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. %We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.
We also remark that {\sc lgo} implements an incomplete BB algorithm for QCQ by using bounds obtained from sampling.
